---
output: github_document
---

<!-- README.md is generated from README.Rmd; please edit the .Rmd file and then from R do rmarkdown::render("README.Rmd")-->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  results = "asis",
  echo = TRUE,
  comment = "#>"
)
IS_README <- TRUE
```

```{r child="docs/mds/intro-logo.md"}

```

# Welcome to Physcraper’s repository!

```{r child="docs/mds/intro-badges.md"}

```

<p></p>

<p></p>


```{r child="docs/mds/intro-part1.md"}

```

Physcraper also leverages on programmatic tools from the [TreeBASE](https://treebase.org/treebase-web/urlAPI.html) project and [NCBI](https://www.ncbi.nlm.nih.gov/home/develop/api/), as well as multiple software projects listed as [requirements](#requirements) below, to create an automatic and reproducible workflow for phylogenetics.

You are now on the code repository. Please refer to Physcraper’s
[documentation website](https://physcraper.readthedocs.io/en/main/)
for more details on:

- [installation](https://physcraper.readthedocs.io/en/main/install.html)
instructions using an Anaconda or a Virtualenv Python virtual
environment,
- [function](https://physcraper.readthedocs.io/en/main/apidocs.html)
usage,
- finding and choosing a [starting dataset](https://physcraper.readthedocs.io/en/main/find-trees.html),
- [running](https://physcraper.readthedocs.io/en/main/run.html) a full analysis,
- [visualizing and analysing](https://physcraper.readthedocs.io/en/main/results.html) results,
- real life [examples](https://physcraper.readthedocs.io/en/main/examples.html), and
- instructions for [developers](https://physcraper.readthedocs.io/en/main/CONTRIBUTING.html), and specifically on how to [update this readme](https://physcraper.readthedocs.io/en/main/CONTRIBUTING.html#updating-the-readme).


:hamster: :palm_tree: :frog: :ear_of_rice: :panda_face: :tulip: :octopus: :blossom: :whale: :mushroom: :ant: :cactus: :fish: :maple_leaf: :water_buffalo: 🦠 :shell: :bug: :octocat:


```{r child="docs/mds/citation.md"}

```


```{r child="docs/mds/license.md"}

```


```{r child="docs/mds/contact.md"}

```


```{r child="docs/mds/updating-the-readme.md"}

```
